Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-27 Moltres.tex
Time steps without hyphen
Substitute new plots from twice refined grid.

The model molten salt reactor closely emulates the \gls{MSRE}. When developing new physics or investigating
different types of transients, one can reduce the model problem to a two
dimensional axisymmetric one for rapid proof of concept. To approximately simulate the lattice
structure of the \gls{MSRE} under 2D conditions, a geometry is constructed with 14 repeating
fuel-moderator regions, as shown in \Cref{fig:geom}. The fuel and moderator
radii are chosen such that the resulting area/volume fraction of fuel is 0.225 as
for the \gls{MSRE}. The 2D mesh has a characteristic size of 10 cm in the axial
direction and .4 cm in the radial direction to capture the variation from moving
between fuel and moderator subdomains. Solution time on the resulting 1960
element, 8697 DOF problem is a couple minutes on a single core. Solving on a
mesh uniformly refined three times yields the same qualitative behavior
described in the results that follow for the coarse mesh. Additionally the 3x
refinement yielded only a 1 K change in the average reactor temperature; thus,
the coarse mesh results are regarded as sufficiently converged.

@@

>>>>

The model molten salt reactor closely emulates the \gls{MSRE}. When developing new physics or investigating
different types of transients, one can reduce the model problem to a two
dimensional axisymmetric one for rapid proof of concept. To approximately simulate the lattice
structure of the \gls{MSRE} under 2D conditions, a geometry is constructed with 14 repeating
fuel-moderator regions, as shown in \Cref{fig:geom}. The fuel and moderator
radii are chosen such that the resulting area/volume fraction of fuel is 0.225 as
for the \gls{MSRE}. The base 2D mesh has a characteristic size of 10 cm in the axial
direction and .4 cm in the radial direction to capture the variation from moving
between fuel and moderator subdomains. To determine whether results were
converged, a mesh convergence study was conducted with up to three levels of isotropic
refinement (e.g. each element was in half in both axial and radial directions,
resulting in four new elements). The metric used to assess convergence was the integrated fast group
flux. The result of the mesh convergence study is shown in
\cref{fig:mesh_convergence}. From refinement level 2 to 3 the metric changes by
only 1\%. We regard the results as sufficiently converged at level 2 for the
purposes of our study; consequently, the results reported in the following
section correspond to a radial element dimension of .1 cm and an axial element
dimension of 2.5 cm.

@@

\begin{figure}[htpb]
  \centering
  \includegraphics{mesh_convergence.eps}
  \label{fig:mesh_convergence}
  \caption{Plot of the integrated fast group flux as the mesh in isotropically refined.}
\end{figure}

### 2017-11-27 revise/revise.tex
Substitute new plots from twice refined grid.

\question It is not clear how the domain is discretized. Is there a radial
discretization in graphite and channels? Was the mesh convergence checked?
Please discuss.
\begin{solution}
       <++>
\end{solution}

>>>>

\question It is not clear how the domain is discretized. Is there a radial
discretization in graphite and channels? Was the mesh convergence checked?
Please discuss.
\begin{solution}
       The following passage and a corresponding figure have been added:

       The base 2D mesh has a characteristic size of 10 cm in the axial
       direction and .4 cm in the radial direction to capture the variation from moving
       between fuel and moderator subdomains. To determine whether results were
       converged, a mesh convergence study was conducted with up to three levels of isotropic
       refinement (e.g. each element was split in half in both axial and radial directions,
       resulting in four new elements). The metric used to assess convergence was the integrated fast group
       flux. The result of the mesh convergence study is shown in
       \cref{fig:mesh_convergence}. From refinement level 2 to 3 the metric changes by
       only 1\%. We regard the results as sufficiently converged at level 2 for the
       purposes of our study; consequently, the results reported in the following
       section correspond to a radial element dimension of .1 cm and an axial element
       dimension of 2.5 cm.
\end{solution}
